Gaps in stellar streams as a result of globular cluster fly-bys

### 2025-05-23 paper/main.tex
tried to make the appendix less confusing

  \salvatore{In the simplest consideration, of two packets of the same dimension $\sigma_x$ and an offset of $\delta x$, the gaps are out of phase when the separation is greater than the width: $1\sim<\sigma_x/\delta x$. Drawing from the wisdom in \citet{2015MNRAS.450.1136E} \& \citet{2016MNRAS.457.3817S}, we see the contrast between the density peaks and the density minimum of a gap, as well as the width, grow in time, somewhere between $\propto \sqrt{t}$ and linear. In this simplified 1D collisionless dispersion analysis, the gaps between the different packets space apart linearly in time with $\delta x\propto \delta vt$, where $\delta v$ is the mean velocity of the about the impact site for two different packets. This inclines us to believe that the gaps space apart before they become significantly deep or wide, however this need not be the general case. }

    \salvatore{Nonetheless, we believe this is the first consideration of decomposing the stream into packets of tidal bursts to understand the effect of the internal dynamics on gap persistence. Since gap persistence depends on the mass and internal evolution of the cluster, characterizing the gap can constrain our knowledge of the internal evolution. }

>>>>

	  \salvatore{The aforementioned analysis highlights the complexity of the conditions on the stream that are necessary for allowing gap formation. Despite this, in the attempts to gain further preliminary insight, we can create an even simpler consideration of a gap created in two different pockets, considering the gaps' drift rates and width, ignoring their density contrasts. If we consider two packets with the same dimensions $\sigma_x$ and an offset of $\delta x$, the gaps are out of phase when the separation is greater than the width: $1\sim<\sigma_x/\delta x$. If $\delta x$ grows much faster than the gap can develop, then the gap is never visible. If the gaps grow in size much faster than their drift rate, then they persist and continue to grow in significance. In the simulations presented in this analysis, we only observe the two extremes and do not produce a case where a significant gap is created to blur out. However, this is not necessarily the general case.}

    \salvatore{Nonetheless, this is a first look at considering the distribution of stream stars originating from shocked outflow, and they allow or disallow gap formation. Fuller considerations would include mass loss from internal dynamics, such as three-body encounters, and a non-constant mass loss rate due to changes in the density distribution resulting from internal mass evolution.}
